Add Plant Functional Type (PFT) labels

### 2021-04-05 R/add_plant_functional_type.Rmd
make parsing code more efficient?

# simplify the growth form into "tree", "shrub", "saplng" etc.  
cleaned_spectra_merged <- cleaned_spectra_merged %>% 
  rowwise() %>%
  # parse out the last word in each entry's growthForm
  mutate(growthForm_simple = rev(strsplit(growthForm, " ")[[1]])[1])

>>>>

# simplify the growth form into "tree", "shrub", "saplng" etc.  
cleaned_spectra_merged <- cleaned_spectra_merged %>% 
  rowwise() %>%
  # parse out the last word in each entry's growthForm
  # make this code more efficient????? 
  mutate(growthForm_simple = rev(strsplit(growthForm, " ")[[1]])[1])
